### 2025-09-12 basic-statistics.qmd
20250911 - clean up code

# plot with ggplot2
ggplot(poly, aes(x,y, fill=id, group=id)) +
  geom_polygon(show.legend=F, alpha=I(8/10)) +
  # add line for treatment group
  geom_line(data=df1, aes(x, y, color = "H0", group = NULL, fill = NULL), linewidth = 1.5, show.legend = FALSE) + 
  # add line for treatment group. These lines could be combined into one dataframe.
  geom_line(data=df2, aes(color = "HA", group = NULL, fill = NULL), linewidth = 1.5, show.legend = FALSE) +
  # add vlines for z_crit
  geom_vline(xintercept = z_crit, linewidth=1, linetype="dashed") +
  # change colors
  scale_color_manual(
    "Group",
    values = c("HA" = "#981e0b", "H0" = "black")) +
  scale_fill_manual("test", values= c("alpha" = "#0d6374", "beta" = "#be805e", "power"="#7cecee")) +
  # beta arrow
  annotate("segment", x = 0.1, y = 0.045, xend = 1.3, yend = 0.01, arrow = grid::arrow(length = unit(0.3, "cm")), linewidth = 1) +
  annotate("text", label="beta", x=0, y=0.05, parse=T, size=8) +
  # alpha arrow
  annotate("segment", x = 4, y = 0.043, xend = 3.4, yend = 0.01, arrow = grid::arrow(length = unit(0.3, "cm")), linewidth = 1) +
  annotate("text", label="frac(alpha,2)", x=4.2, y=0.05, parse=T, size=8) +
  # power arrow
  annotate("segment", x = 6, y = 0.2, xend = 4.5, yend = 0.15, arrow = grid::arrow(length = unit(0.3, "cm")), linewidth = 1) +
  annotate("text", label = "1 - beta ~ '(power)'", x = 6.1, y = 0.21, parse = TRUE, size = 8) + 
  # H_0 title
  annotate("text", label = "H[0]", x = m1, y = 0.28, parse = TRUE, size = 8) +
  # H_a title
  annotate("text", label = "H[1]", x = m2, y = 0.28, parse = TRUE, size = 8) +
  ggtitle("Statistical Power") +
  # remove some elements
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    panel.background = element_blank(),
    plot.background = element_rect(fill="white"),
    panel.border = element_blank(),
    axis.line = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(size=22))
```

>>>>

# plot with ggplot2
ggplot(
  poly,
  aes(
    x,
    y,
    fill = id,
    group = id)) +
  geom_polygon(
    show.legend = FALSE,
    alpha = I(8/10)) +
  # add line for treatment group
  geom_line(
    data = df1,
    aes(
      x,
      y,
      color = "H0",
      group = NULL,
      fill = NULL),
    linewidth = 1.5,
    show.legend = FALSE) + 
  # add line for treatment group. These lines could be combined into one dataframe.
  geom_line(
    data = df2,
    aes(
      color = "HA",
      group = NULL,
      fill = NULL),
    linewidth = 1.5,
    show.legend = FALSE) +
  # add vlines for z_crit
  geom_vline(
    xintercept = z_crit,
    linewidth = 1,
    linetype = "dashed") +
  # change colors
  scale_color_manual(
    "Group",
    values = c("HA" = "#981e0b", "H0" = "black")) +
  scale_fill_manual(
    "test",
    values = c("alpha" = "#0d6374", "beta" = "#be805e", "power"="#7cecee")) +
  # beta arrow
  annotate(
    "segment",
    x = 0.1,
    y = 0.045,
    xend = 1.3,
    yend = 0.01,
    arrow = grid::arrow(length = unit(0.3, "cm")),
    linewidth = 1) +
  annotate(
    "text",
    label = "beta",
    x = 0,
    y = 0.05,
    parse = TRUE,
    size = 8) +
  # alpha arrow
  annotate(
    "segment",
    x = 4,
    y = 0.043,
    xend = 3.4,
    yend = 0.01,
    arrow = grid::arrow(length = unit(0.3, "cm")),
    linewidth = 1) +
  annotate(
    "text",
    label = "frac(alpha,2)",
    x = 4.2,
    y = 0.05,
    parse = TRUE,
    size = 8) +
  # power arrow
  annotate(
    "segment",
    x = 6,
    y = 0.2,
    xend = 4.5,
    yend = 0.15,
    arrow = grid::arrow(length = unit(0.3, "cm")),
    linewidth = 1) +
  annotate(
    "text",
    label = "1 - beta ~ '(power)'",
    x = 6.1,
    y = 0.21,
    parse = TRUE,
    size = 8) + 
  # H_0 title
  annotate(
    "text",
    label = "H[0]",
    x = m1,
    y = 0.28,
    parse = TRUE,
    size = 8) +
  # H_a title
  annotate(
    "text",
    label = "H[1]",
    x = m2,
    y = 0.28,
    parse = TRUE,
    size = 8) +
  ggtitle("Statistical Power") +
  # remove some elements
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    panel.background = element_blank(),
    plot.background = element_rect(fill = "white"),
    panel.border = element_blank(),
    axis.line = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(size = 22))
```
